Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-06-04 Masterarbeit_Robotik_Pamuk.tex
minor

\noindent The statistics obtained from this measurement are provided in Table \ref{tab:latency_statistics}. It gives an overview of the average, maximum, minimum latency, and the standard deviation of the latency values in microseconds.

\begin{table}[h]
	\centering
	\caption{Latency Statistics in microseconds}
	\label{tab:latency_statistics}
	\begin{tabular}{|c|c|}\hline
	\textbf{Statistic} & \textbf{Value (\textmu s)} \\\hline
	Average Latency & 4.06 \\\hline
	Maximum Latency & 10.71 \\\hline
	Minimum Latency & 2.82 \\\hline
	Standard Deviation & 0.85 \\\hline
	\end{tabular}
	\end{table}

@@

\noindent The statistics obtained from this measurement are provided in Table \ref{tab:x}. It gives an overview of the average, maximum, minimum latency, and the standard deviation of the latency values in microseconds.

\begin{table}[h]
	\centering
	\caption{Latency Statistics default in microseconds}
	\label{tab:x}
	\begin{tabular}{|c|c|}\hline
	\textbf{Statistic} & \textbf{Value (\textmu s)} \\\hline
	Average Latency & 46.22 \\\hline
	Maximum Latency & 707.62 \\\hline
	Minimum Latency & 15.59 \\\hline
	Standard Deviation & 52.13 \\\hline
	\end{tabular}
	\end{table}

@@

\clearpage
\chapter{Real-Time Performance Tuning}\label{cha:real-time_tuning}
\section{BIOS Configurations}
BIOS is firmware used to perform hardware initialization during the booting process. Some BIOS settings can have a significant impact on the real-time performance of the system [2]. The configurations in Table 4 are tuned for real-time performance.

@@

The kernel command-line parameters [6] are shown in Code \ref{script:kernel_cli} below. Some of them are essential for real-time performance.

>>>>

\noindent The statistics obtained from this measurement are provided in Table \ref{tab:latency_statistics_bare_metal}. It gives an overview of the average, maximum, minimum latency, and the standard deviation of the latency values in microseconds.

\begin{table}[h]
	\centering
	\caption{Latency statistics of Salamander 4 bare metal in microseconds}
	\label{tab:latency_statistics_bare_metal}
	\begin{tabular}{|c|c|}\hline
	\textbf{Statistic} & \textbf{Value (\textmu s)} \\\hline
	Average Latency & 4.06 \\\hline
	Maximum Latency & 10.71 \\\hline
	Minimum Latency & 2.82 \\\hline
	Standard Deviation & 0.85 \\\hline
	\end{tabular}
	\end{table}

@@

\noindent The statistics obtained from this measurement are provided in Table \ref{tab:latency_statistics_virt}. It gives an overview of the average, maximum, minimum latency, and the standard deviation of the latency values in microseconds.

\begin{table}[h]
	\centering
	\caption{Latency statistics of default Salamander 4 virtualization in microseconds}
	\label{tab:latency_statistics_virt}
	\begin{tabular}{|c|c|}\hline
	\textbf{Statistic} & \textbf{Value (\textmu s)} \\\hline
	Average Latency & 46.22 \\\hline
	Maximum Latency & 707.62 \\\hline
	Minimum Latency & 15.59 \\\hline
	Standard Deviation & 52.13 \\\hline
	\end{tabular}
	\end{table}

@@

\clearpage
\chapter{Real-Time Performance Tuning}\label{cha:real-time_tuning}
\section{BIOS Configurations}
BIOS is firmware used to perform hardware initialization during the booting process. Some BIOS settings can have a significant impact on the real-time performance of the system. The configurations in Table 4 are tuned for real-time performance.

@@

The kernel command-line parameters are shown in Code \ref{script:kernel_cli} below. Some of them are essential for real-time performance.
